Multiset-trie data structure

### 2019-03-06 tex/tex/s_experiments.tex
Inline answers to comments

%% more details about implementation of the inverted files
((Presentation of the inverted index implementation? What about the smallest postings first?))

@@

((Is there anything special to be said about the artificially generated data?))

@@

We can see that multiset-trie outperforms inverted index in all of the experiments by up to 4 orders of magnitude. In an exact search, multiset-trie has to traverse only up to $\sigma+1$ nodes to get query result. It can be seen from results that with the increase of $\sigma$ the processing time for multiset-tire also increases. Multiplicity also affects the processing time; however, this happens passively. ((equivalent to $\sigma+1$?)) Multiplicity, or degree of a node $n$, defines the shape of multisets that are stored in multiset-trie. Thus, it affects the structure and density of the multiset-trie.

As for the inverted index, all three operations must first fetch all the postings for each particular element of a test multi-set. Afterward, the intersection of postings is computed to answer the query. The operations use more processing time than a simple tree traversal, which we can see from results. Postings are filtered on-the-fly to reduce the cost of the intersection. ((I do not get this: "Note that inverted index will also access at most $\sigma$ postings during search, but in addition to access some extra processing is required."))

@@

%% more details on this paragraph
((Can you characterize the sub-tree (num of nodes visited) visited by an operation more precisely? Can we say something about this? What is the size of the sub-tree visited by an operation? Why it is not very large? I did not try to finalize the following text.))
In the case of multiset-trie, only a traversal of the tree is required which is much faster than the processing of postings as we can see from results. In the worst case the whole tree is traversed, but so is for an inverted file. ((Can we see how...?))

>>>>

%% more details about implementation of the inverted files
((Presentation of the inverted index implementation? What about the smallest postings first?) -- (What do you mean by "smallest postings"?))

@@

((Is there anything special to be said about the artificially generated data?) -- (Not really. We say that the data is generated with respect to ms-trie parameters and it is random. Other detail, such as how we generated the data (with Python) does not really matter.))

@@

We can see that multiset-trie outperforms inverted index in all of the experiments by up to 4 orders of magnitude. In an exact search, multiset-trie has to traverse only up to $\sigma+1$ nodes to get query result. It can be seen from results that with the increase of $\sigma$ the processing time for multiset-tire also increases. Multiplicity also affects the processing time; however, this happens passively. ((equivalent to $\sigma+1$?) -- (No, much smaller impact. In fact, if we consider the same data set and vary $\sigma$ and max multiplicity, the multiplicity will have almost no influence. The $\sigma$ will affect every single lookup of a multiset in ms-trie, when multiplicity will only influence supermultiset queries, where we will check one extra multiplicity.)) Multiplicity, or degree of a node $n$, defines the shape of multisets that are stored in multiset-trie. Thus, it affects the structure and density of the multiset-trie.

As for the inverted index, all three operations must first fetch all the postings for each particular element of a test multi-set. Afterward, the intersection of postings is computed to answer the query. The operations use more processing time than a simple tree traversal, which we can see from results. Postings are filtered on-the-fly to reduce the cost of the intersection. ((I do not get this: "Note that inverted index will also access at most $\sigma$ postings during search, but in addition to access some extra processing is required.") -- (Inverted index will search for multisets in all of the postings ($\sigma$ postings) in the worst case. Ms-trie needs to traverse $\sigma + 1$ nodes to lookup a multiset. So the access time would be approximately the same. However, inverted index requires additional processing of postings to search for a multiset when the ms-trie does not.))

@@

%% more details on this paragraph
((Can you characterize the sub-tree (num of nodes visited) visited by an operation more precisely? Can we say something about this? What is the size of the sub-tree visited by an operation? Why it is not very large? I did not try to finalize the following text.) -- (The sub-tree we visit is quite simple to picture. Take a multiset and draw the complete path defined by this multiset in the ms-trie. Everything that is on the left side of this path will be visited by submset query, everything on the right will be visited by supermset query. The size of this sub-tree we actually described in the math analysis. There is a formula that is parameterized by input multiset. I think I don't say that it is not large anywhere. It can be the whole tree.))
In the case of multiset-trie, only a traversal of the tree is required which is much faster than the processing of postings as we can see from results. In the worst case the whole tree is traversed, but so is for an inverted file. ((Can we see how...?) -- (The same way as with ms-trie. Just search for a submsets of some large multiset that would result in retrieving the whole structure.))
